Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-08 paper/main.tex
cleaning comments and supplementals

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
    % our audience highlighting innovative examples of data reuse may be used to
    % present compelling new findings & conclusions derived from published.
    % intro
Neuroimaging studies have parcellated the human brain into distinct functional
    areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
    is classically considered to be a higher visual area as increased
    hemodynamic activity in the PPA correlates with the perception of static
    pictures of landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize spatial
    perception\todo{not sure if this is just perception} in 14 subjects that
    were watching an audio-visual Hollywood movie and listened to the movie's
    audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we test if an auditory narrative could
    localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
    general linear model (GLM) $t$-contrasts that are based on annotations of
    selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
    that we conducted previously to localize the PPA in the same participants.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.  results: group AV
On a group level, results for a visual movie stimulus show significantly
    increased hemodynamic activity spatially overlapping with a traditionally
    localized PPA but also extending into earlier visual cortices.
% results: group AD
Results for the audio-description stimulus reveal significant activation
    restricted to the anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
    bilateral clusters in the anterior PPA of nine subjects and significant
    unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
    static pictures generalizes to the perception of spatial information
    embedded in an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provide further evidence that the PPA can be divided into functional
    subregions.
% localizer substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
    anterior part in visually impaired subjects.\todo{very bold claim to be
    written in the abstract}

\end{abstract}

@@

\begin{itemize}
    \item in case the additional contrast stay in supplemental material, just
        speak of contrast not ``primary contrast''
    \item adopt some phrasing from the Speech-Anno-Paper
    \item there is no "cue about" in the English language? Alternatives are
        "give a hint on/about", "indicate"; changed the sentences but should
        ask Alex
\end{itemize}

@@

\noindent Discussion
\begin{itemize}
    \item as Simon stated I would be interesting to discuss differences between
        contrasts (and make wild assumptions) but this will exceed the word
    limit by far
    \item overall conclusion as a last paragraph or independent section
\end{itemize}

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} compared hemodynamic
activity levels in the PPA that were correlated with differrent semantic
categories occurring in spoken language.
% Aziz' stimuli; ``The Taj Mahal faces a long thin reflecting pool'', ``Marilyn
% Monroe has a large square jaw'', ``The television has a long antenna''
\cite{aziz2008modulation} used sentences that described famous or generic places
and faces, or objects.\todo{judgment task not mentioned anymore}
% Aziz' tasks: Participants were instructed to press a button whenever the
% sentence described an inaccurate or improbable fact. Aziz' results:
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
All reviewed studies share three common aspects:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-design paradigms to maximize detection power.
Further, they usually employed an explicit (perceptual) judgment task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantage of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of a[n
explicit] perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Lastly, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approach improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

@@

\subsection{Event selection}

@@

% irrespective of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables.
% AV COPEs: intro
The rationale that this approach would yield categories that - on average - show
different stimulus features.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Later in the movie when the spatial layout of a setting is already established,
shots within a setting shift to objects more relevant to the evolved plot and or
to switching between faces of persons talking to each others (\texttt{vpe\_old})
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points
\citep{epstein1999parahippocampal, grill2006repetition}.\todo[inline]{doesn't
make sense not 'cause this should be true to the face of forrest too}
% no cut condition: intro
In order to create a control condition, a sixth category (\texttt{no\_cut}) was
created by pseudo-randomly drawing movie frames from continuous movie shots that
lasted longer than \unit[20]{s}.
% no cuts: how
Events were drawn from movie shots in such a way that each event had a minimum
temporal distance of at least \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

% AD annotation
For the analysis of the AD stimulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, the rule for a word to belong to
a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a
small amount of counts were pooled resulting in 11 final event categories (see
Table \ref{tab:ao-events}). These event categories were then used to model
hemodynamic responses.

@@

\todo[inline]{SE: würde wetten, dass Reviewer fragen: Wie sieht es im vergleich
dazu mit Faces aus? COH: yeah, well, I made the contrasts similar to Sengupta
and considered the contrast to an average of all ``non-spatial'' stuff
appropriate; should be cleare in the method section (s. ``Contrasts'')}

@@

% similar to previous studies
On the first level, we created GLM contrasts like studies that contrasted blocks
of pictures.
% dissimilar
But unlike previous studies, our approach was to contrast selected stimulus
features that we annotated in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) and eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts})
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
(2010) Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /

% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vse\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that category \texttt{vse\_new} on average comprised the most movie
frames depicting a landscape or the geometry of a setting, and the category
\texttt{vpe\_old} the most frames depicting persons, faces, or
objects.\todo{maybe speak of ratio}
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture} to get a sufficient amount of events per stimulus segment.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already indicate a change of settings.
\todo[inline]{paragraph above could state that ``fahead'', just N=83; mostly
    just parts (``ear'', ``nose'') of face, or vague description ``his/her
face''}.
% control contrasts
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory hint of switching to another
setting.
%
\todo[inline]{it's probally not about the soundscape anymore (to speculative)
but about the somewhat correlation of nouns and cuts}

@@

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see \ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus AD) of
two spatially corresponding voxels in the unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

@@

\subsection{Robustness of group results across contrasts}

% unthresholded $z$-maps of all contrasts on a group level:
% \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.

@@

% AV
In order to test the robustness of our findings, we created four additional
$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
investigated on a group level.
% results: PPA; biggest overlap in posterior part of PPA group overlap  =
%temporal occipital fusiform cortex
All of the overall five AV contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
% AD
For the AD stimulus, we created overall eight $t$-contrasts (see Table
\ref{tab:ao-contrasts}).
% results
All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
categories) yielded significant bilateral clusters in anterior regions of the
group PPA overlap (see Figure \ref{fig:stability-slices}), suggesting
a certain robustness of this result.

@@

% AD
Reliably across the five contrasts of the AV stimulus, we find bilaterally
significant clusters also in the ventral precuneal cortex and posterior
cingulate gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral
occipital cortex (contrasts 1, 2, 4, 5).
% AD; LOC: AV cluster are more medial, AD clusters are more lateral
Across the five contrasts of the AD stimulus, we find bilaterally
significant clusters in the ventral precuneus (all except contrasts 8), lateral
occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
right in contrast 2).

% non-systematic
Lastly, some contrasts of the AD stimulus yielded signficant clusters in regions
that were not statistically signficant in three or more contrasts.
%
Contrast 2 yielded clusters in the anterior cingulate gyrus
(bilateral), right frontal pole, right frontal medial cortex, and right
putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum
[border to triangularis], left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.

@@

\subsection{control contrasts}

@@

\todo[inline]{there is no table/figure for negative control contrasts; we could
add a reference to NeuroVault (here again) or point to the dataset}

% intro
Lastly, we implemented five contrasts for every stimulus for the purpose of
negative control.
% AV: no_cut > x
In the analysis of the AV data, none of the contrasts that compared the ``no cut
condition''  to a movie cut category (contrasts 6, 7, 8, 9) yielded significant
clusters.
% AV using nouns
The contrast that used the narrator's nouns but in the AV stimulus
(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
PPA and bilateral clusters in the superior lateral occipital cortices (the right
hemispheric cluster extending into the superior parietal cortex).

% AD stimulus
In the analysis of the AD data, we created control contrasts based on events of
the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
% contrast 9
Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.

\subsection{Discussion: Robust results across contrasts}

>>>>

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize the perception of
spatial information in 14 subjects that were watching an audio-visual Hollywood
movie and listened to the movie's audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we test if an auditory narrative could
localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on annotations of
selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.  results: group AV
On a group level, results for a visual movie stimulus show significantly
increased hemodynamic activity spatially overlapping with a traditionally
localized PPA but also extending into earlier visual cortices.
% results: group AD
Results for the audio-description stimulus reveal significant activation
restricted to the anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provide further evidence that the PPA can be divided into functional
subregions.
% localizer substitute
[An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.]
\end{abstract}

@@

\begin{itemize}
    \item in case the additional contrast stay in supplemental material, just
        speak of contrast not ``primary contrast''
    \item in main text, add references to supplemental material
    \item there is no "cue about" in the English language? Alternatives are
        "give a hint on/about", "indicate"; changed the sentences but should
        ask Alex
\end{itemize}

@@

\noindent Discussion
\begin{itemize}
    \item summary \& overall conclusion (last paragraph or independent section)
\end{itemize}

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} compared hemodynamic
activity levels in the PPA that were correlated with differrent semantic
categories occurring in spoken language.
% Aziz' stimuli; ``The Taj Mahal faces a long thin reflecting pool'', ``Marilyn
% Monroe has a large square jaw'', ``The television has a long antenna''
\cite{aziz2008modulation} used sentences that described famous or generic places
and faces, or objects.
% Aziz' tasks:
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact (e.g. ``Marilyn Monroe has a large square
jaw'')
% Aziz' results:
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
All reviewed studies share three common aspects:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-design paradigms to maximize detection power.
Further, they usually employed an explicit (perceptual) judgement task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantage of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of a[n
explicit] perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Lastly, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approach improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

@@

\subsection{Event selection} \label{rationale}

@@

% irrespective of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables.
% AV COPEs: intro
The rationale that this approach would yield categories that - on average - show
different stimulus features.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Later in the movie when the spatial layout of a setting is already established,
shots within a setting shift to objects more relevant to the evolved plot and or
to switching between faces of persons talking to each others (\texttt{vpe\_old})
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points
\citep{epstein1999parahippocampal, grill2006repetition}.
%
\todo{imo its better to focus on the cinematographic rationale and drop the last
sentence 'cause activity in e.g. FFA adopts too -> we might substract an on
average smaller response}
% no cut condition: intro
In order to create a control condition, a sixth category (\texttt{no\_cut}) was
created by pseudo-randomly drawing movie frames from continuous movie shots that
lasted longer than \unit[20]{s}.
% no cuts: how
Events were drawn from movie shots in such a way that each event had a minimum
temporal distance of at least \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

% AD annotation
For the analysis of the AD stimulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of (concrete and countable) nouns that
the narrator uses to describe the movie's missing visual content based on a set
of rules.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, the rule for a word to belong to
a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (see Table
\ref{tab:ao-events}). These event categories were then used to model hemodynamic
responses.

@@

\todo[inline]{SE: Vergleich zu Faces aus? COH: should be clearer now why we did
not do it}

@@

% similar to previous studies
On the first level, we created GLM contrasts based on annotated stimulus
features embedded in the in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) and eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts})
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
% (2010)
Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) the amount of available data, b) how
well the average of events within represented spatial information and
non-spatial information respectively (cf. section \ref{rationale}).
% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vse\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that category \texttt{vse\_new} on average comprised the most movie
frames depicting a landscape or the geometry of a setting, and the category
\texttt{vpe\_old} the most frames depicting persons, faces, or objects [(cf.
rationale to categorize the cuts in section \ref{rationale})].
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture} to get a sufficient amount of events per stimulus segment.
\todo[inline]{in detail: \texttt{fahead}: just N=83; mostly parts
 of face (``ear'', ``nose''), or vague description (``his/her face''; N=10)}
% why furniture was not used
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
[c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already indicate a change of settings.] \todo[inline]{for
sake of conciseness, it is imo better to drop that ``soundscape-thing''}
% control contrasts
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory hint of switching to another
setting.
%
\todo[inline]{it's probally not about the soundscape anymore (to speculative)
but about the somewhat correlation of nouns and cuts}

@@

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see Figure \ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus AD) of
two spatially corresponding voxels in the unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axes
in Figure \ref{fig:bland-altman}).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

@@

\todo[inline]{I think it makes sense to report results of AV and discuss AV,
and then report results of AD and discuss AD}

\subsection{Results}

\subsubsection{Robustness of group results across contrasts}

% intro
In order to test the robustness of our approach, we created overall five
$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}), and
overall eight $t$-contrast for the AD stimulus (see Table
\ref{tab:av-contrasts}) by varying the contrasted categories (and thus the
amount of available data), and how well the annotated events within categories
on average matched a stimulus type that we assumed to correlate with spatial
perception.
% NeuroVault
Unthresholded z -maps of all contrasts on a group level as well as individual
results of the primary t-contrasts co-registered to the group-template (MNI152
space) can found at NeuroVault
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.

@@

% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
% temporal occipital fusiform cortex
All five AV contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
% AV: RSC & LOC
Reliably across contrasts of the AV stimulus, we find bilaterally
significant clusters also in the ventral precuneal cortex and posterior
cingulate gyrus (i.e. restrosplenial complex; contrasts 1, 4, 5), and lateral
occipital cortex (contrasts 1, 2, 4, 5).

@@

% AD: results
In results of the AD stimulus, all contrasts except contrast 7
(\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and contrast 8
(\texttt{se\_new} > non-spatial categories) yielded significant bilateral
clusters in anterior regions of the group PPA overlap (see Figure
\ref{fig:stability-slices}).
% AD: RSC & LOC
Reliably across contrast of the AD stimulus, we find bilaterally significant
clusters also in the ventral precuneus (all except contrasts 8), lateral
occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
right in contrast 2).
% non-systematic
Lastly, some contrasts of the AD stimulus yielded signficant clusters in regions
that were not statistically signficant in three or more contrasts.
%
Contrast 2 yielded clusters in the anterior cingulate gyrus
(bilateral), right frontal pole, right frontal medial cortex, and right
putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum
[border to triangularis], left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.

@@

\subsubsection{control contrasts}

% intro
For the purpose of negative control, we implemented five contrasts for every
stimulus.

@@

% AV: no_cut > x
In the analysis of the AV data, none of the four contrasts that compared the
\texttt{no\_cut} categorie to a movie cut category (see Table
\ref{tab:av-contrasts}) yielded significant clusters.
% AV using nouns
The contrast that used the narrator's nouns but in the AV stimulus
(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
PPA and bilateral clusters in the superior lateral occipital cortices (the right
hemispheric cluster extending into the superior parietal cortex).\todo{cuts
correlate with the nouns}

% AD stimulus
In the analysis of the AD data, we created control contrasts based on events of
the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
% contrast 9
Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.\todo{odd imo}

\subsection{Discussion}

\subsubsection{congruencies (PPA, RSC, LOC, others)}
